### 2019-08-06 README.Rmd
prepared for meeting with Heike

- adding a random noise variable to the model to see if LIME ever chooses it as an important variable
- can I remove some of the sources from the references file that I am not going to use?

@@

- draft background section
- read through papers giving an overview of the current explanation methods
- create first draft of JSM poster

>>>>

JSM

- Lots of "enthusiasm" about interpreting random forest models from individuals who stopped by the poster (the next presenter had to ask me to leave)
- Many people seemed to agree that just using the default values of LIME will not be enough to necessarily capture the local trend
- Shapley values were mentioned several times
- See email from Shar (references and possible collaborator)
- I think I may have convinced Adam to talk at graphics group if we end up scheduling graphics group on Thursday
- Saw Andrew - he has invited me to give a talk at Lawrence this winter
- I updated my website while at JSM
- I realized that I left the CSAFE logo off the poster. Should I always include this to acknowledge that there were the source of funding for the dataset?

SAMSI

- Have you heard of trelliscope: https://hafen.github.io/trelliscopejs/#trelliscope
- Opinions on saving pdf files to github - if no - what to do?

NCCC

- Adding a random noise variable to the model to see if LIME ever chooses it as an important variable

Paper

- Can I remove some of the sources from the references file that I am not going to use?
- Have you heard of: Journal of Data Science, Statistics, and Visualisation (jdssv.org)
- What are your recommendations for going forward in the month of August? 
- Should we start talking about a date for my oral prelim?

@@

- draft background section
- read through papers giving an overview of the current explanation methods
